FAO salmon production

### 2021-05-11 analysis/paper_stats.Rmd
made the figures!

>>>>

all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")

unique(sort(all_farms$country))

all_known_locations <- all_farms %>%
  filter(data_type == "known location")

unique(all_known_locations$country)

## read in each of the comprehensive locations

farms_folder <- file.path("aquaculture_mapping/marine")

bivalve_comp_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5"), full=TRUE)

bivalve_comp <- plyr::ldply(bivalve_comp_files, read_csv) %>%
  mutate(type = "bivalve") %>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

shrimp_comp_files <- list.files(here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5"), full=TRUE)

shrimp_comp <- plyr::ldply(shrimp_comp_files, read_csv) %>%
  mutate(type = "shrimp")%>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

salmon_comp_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)

salmon_comp <- plyr::ldply(salmon_comp_files, read_csv) %>%
  mutate(type = "salmon")%>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

tuna_comp_files <- list.files(here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)

tuna_comp <- plyr::ldply(tuna_comp_files, read_csv) %>%
  mutate(type = "tuna")%>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

finfish_comp_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5"), full=TRUE)

finfish_comp <- plyr::ldply(finfish_comp_files, read_csv) %>%
  mutate(type = "finfish")%>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

crustaceans_comp_files <- list.files(here("marine/crustaceans/crustaceans_farms/data/known_farm_sites_2_4_5"), full=TRUE)

crustaceans_comp <- plyr::ldply(crustaceans_comp_files, read_csv) %>%
  mutate(type = "crustaceans")%>%
  dplyr::select(lat, lon, iso3c, data_quality, type)

all_comp_farms <- rbind(finfish_comp, bivalve_comp, salmon_comp, tuna_comp, shrimp_comp) %>%
  filter(data_quality == 5) %>%
  group_by(iso3c, type) %>%
  summarise(n_obs = n())

unique(all_comp_farms$iso3c)

## Countries that have comprehensive location data across all their species reported:
# - ARE (1 type), GRC (2 type), MLT (2 types), NOR (3 types), CYP (1 type), HKG (2 type), BLG (1 type), BLZ (1 type), CAN (2 types), CHL (2 types), DNK (2 types), FIN (1 type), FRO (1 type), GBR (2 types), IRL (2 types), JEY (1 type)
```

### 2021-05-11 marine/STEP1_species_groups/STEP1_species_groups.Rmd
wrote READMEs and cleaned up organization
made the figures!

fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
  dplyr::filter(value >= 500) %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup() %>%
  # dplyr::filter(tonnes >= 500) %>%
  group_by(country, aq_group, year) %>%
  summarise(total_tonnes = sum(tonnes)) %>%
  arrange(aq_group)

@@

test <- fao_1 %>%
  dplyr::filter(aq_group == "bivalves")
sum(test$total_tonnes) # 17435623

>>>>

fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
  # dplyr::filter(value >= 500) %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup() %>%
  # dplyr::filter(tonnes >= 500) %>%
  group_by(country, year) %>%
  summarise(total_tonnes = sum(tonnes))# %>%
 # arrange(aq_group)

@@

## Take a look at the data 
test <- fao_1 %>%
  dplyr::filter(aq_group == "bivalves")
sum(test$total_tonnes) # 17435623

### 2021-05-11 marine/crustaceans/crustaceans_farms/STEP1_fao_crustacean_production.Rmd
made the figures!

@@

>>>>

sum(explore$fao_tonnes_production) # 401719.1
unique(explore$country) # 6 countries

@@

```{r}
## write out bivalve taxa and production for Juliette
fao_crustaceans_taxa_prod <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_crustaceans_taxa_prod$value) # 401733.5 - adds 14 tonnes

unique(fao_crustaceans_taxa_prod$country) # 6 countries 
```

### 2021-05-11 marine/crustaceans/crustaceans_farms/STEP2_crustacean_farm_locations.Rmd
made the figures!

Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

## Indonesia
Can't find any infomration on crab farm locations in Indonesia. I will place one farm, randomly on the coast of Indonesia.

@@

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_idn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_idn.csv"))

## visualize it 
farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_idn)
```

@@

Can't find any datasets of marine crustacean farm locations in China. I will place one farm randomly on the coast of China.

@@

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

write_csv(farms_chn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_chn.csv"))

## visualize it 
farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_chn)
```

@@

 - I'll place points in the Khulna and Chittagong regions, since I can't find any other information on mud crab aquaculture locations in Bangladesh.

 - Khulna: 21.876081791221054, 89.49499697244659
 - Chittagong: 22.325919306644522, 91.76441856678511

@@

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
                        lon = c(89.49499697244659, 91.76091935028879)) %>%
  mutate(iso3c = "BGD") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability",
         subregion = c("Khulna", "Chittagong"))

write_csv(farms_bgd, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_bgd.csv"))

## visualize it 
farms_bgd <-  st_as_sf(farms_bgd, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bgd)
```

@@

 - I'll place points in Ayeyarwaddy region and Rakhine state.
 - Ayeyarwaddy: 15.930407995930784, 94.76647475697742
 - Rakhine: 18.615093163569437, 94.24290607527016

@@

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability",
         subregion = c("Ayeyarwaddy", "Rakhine"))

write_csv(farms_mmr, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_mmr.csv"))

## visualize it 
farms_mmr <-  st_as_sf(farms_mmr, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mmr)
```

@@

 - Table on page 20: This is a table from 2004, but it will have to do. It also has production estimates, which is nice. I will randomly place a point along the coast in each province, and allocate the production accordingly in step 3.. 
  - NOTE: for the production, we are assuming that not reported within a province == 0 production, due to the lack of data.

  - Quang Ninh: prod = 0: 21.186050529545593, 107.60858937642442
  - Hai Phong: prod = 1650: 20.840947248646557, 106.77685003845498
  - Thai Binh: prod = 0: 20.454148639095266, 106.59728856581118
  - Nam Dinh: prod = 0: 20.146554460540862, 106.3298019452741
  - Ninh Binh: prod = 1005: 19.955496263213185, 106.03097468374126
  - Thanh Hoa: prod = 970: 19.726817666482322, 105.87661730467457
  - Nghe An: prod = 0: 18.982876968029743, 105.6165097440173
  - Ha Tinh: prod = 200: 18.456817613512555, 105.92726656633255
  - Quang Binh: prod = 110: 17.56001328746647, 106.58039999954293
  - Quang Tri: prod = 20: 16.905826522213328, 107.19194145855845
  - TT Hue: prod = 82: 16.495115996149718, 107.74891583338649
  - Da Nang: prod = 0: 16.167986126005765, 108.15075180169012
  - Quang Nam: prod = 135: 15.699026568754403, 108.48016289264334
  - Quang Ngai: prod = 0: 15.010595152983287, 108.92174225624275
  - Binh Dinh: prod = 130: 14.17668770026659, 109.19617116389627
  - Phu Yen: prod = 0: 13.335760529041393, 109.29183511586322
  - Khanh Hoa: prod = 0: 12.299111935360338, 109.23699322130719
  - Ninh Thuân: prod = 5: 11.62183927318579, 109.1546891359726
  - Binh Thuân: prod = 0: 10.830102342204183, 108.03702110643216
  - Long An: prod = 250: 10.510731358280973, 106.7310999868549
  - Tien Giang: prod = 0: 10.30006571666483, 106.78122716883196
  - Ben Tre: prod = 637: 10.037866832581582, 106.69637036338817
  - Tra Vinh: prod = 1196: 9.592223563185232, 106.54126727713718
  - Soc Trang: prod = 0: 9.389580381208823, 106.1857446280396
  - Bac Lieu: prod = 3466: 9.147921315425062, 105.59613926925006
  - Ca Mau: prod = 0: 8.674166818318303, 105.12379673906345
  - Kien Giang: prod = 170: 10.087872204898957, 104.88743812284027
  - Can Tho: prod = 0: 10.055231, 105.789267

@@

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), subregion = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_vnm, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_vnm.csv"))

## visualize it 
farms_vnm_map <-  st_as_sf(farms_vnm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_vnm_map)
```

@@

 - I've saved the table in Aurora as a .csv.

 - I'll place a point in each location listed in the table, and use the production estimates to allocate the FAO production equally (although the number is almost the same as reported in the FAO, off by 3 tonnes).

@@

```{r}
phl_mudcrab_prod <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Philippines/phl_mudcrab_production.csv")) %>%
  dplyr::select(-X6) %>%
  mutate(`2017` = as.numeric(`2017`), 
         `2018` = as.numeric(`2018`),
         `2019` = as.numeric(`2019`)) %>%
  pivot_longer(cols = c(`2017`, `2018`, `2019`), names_to = "year", values_to = "prod") %>%
  dplyr::filter(!is.na(prod), 
                year == 2017)

## now we need to find coordinates for each province. I will randomly select a lat lon point along the coast of each province:

provinces <- data.frame(Province = unique(sort(phl_mudcrab_prod$Province))) %>%
  mutate(lat_lon = c("9.190611500208238, 125.52994229122065", "11.737731148020183, 122.36341263788152", "13.21836252920181, 123.77011641931539", "11.096612509189843, 122.04466274447995", "14.588280500720717, 120.39232212075018", "10.062398891617871, 124.08857333922121", "14.759345796261423, 120.79195178365572", "14.278379190276917, 122.80695157663077", "13.728018225223346, 123.21602051808212", "11.544441602769396, 122.87251489793287", "13.600373850277089, 124.08856214435265", "7.226273453773761, 125.8615542691359", "7.29064081849023, 125.70838297490391", "6.8067269257546394, 125.38044959114181", "7.021850825639651, 126.44668668618641", "10.249781995409927, 125.64231490812028", "11.457019560196713, 125.50124809292508", "18.35920136671901, 121.62457647441146", "14.294681717859676, 120.71661934172276", "10.565159685797113, 122.51279683720878", "16.5330902343553, 120.31511351999148", "8.187575265346036, 124.12440346213432", "10.86506672011331, 124.72028684317488", "17.08773382905305, 120.43638606220428", "17.205031284221167, 120.4139227279512", "10.891325726593882, 122.7831164266059", "6.994603962157642, 123.99059538388416", "13.344206870917525, 121.82133665840661", "12.576951933159716, 123.28286940887746", "14.510536378070825, 121.08748285435844", "8.483931963597566, 123.80942490173003", "8.846965587470466, 125.16333794567215", "9.943820309588942, 122.44630440874657", "12.509837523018708, 124.65010656730024", "13.415437014491157, 121.0922973705213", "10.038412865363988, 118.7206892394855", "14.855971440318308, 120.58766325017285", "16.124387999329027, 120.09336724359946", "14.664908885542868, 121.61549543341468", "12.585717059110207, 122.27016916837972", "12.007625357698121, 124.69126813617964", "12.818661572681938, 123.83950186846029", "6.373081834977807, 124.08215994073517", "9.555721530351239, 125.78630860627861", "9.013346905513, 126.23742298508941", "6.9053988560744335, 122.0691745144182", "8.18224915422801, 122.95491554623727", "7.81172076996685, 123.42354992829671", "7.703880319874889, 122.52615049321432", "15.272079732639275, 120.00987788280406")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",")

## Now join together with our larger dataset

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "subregion" = "Province") %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(phl_lat_lon, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_phl.csv"))

## visualize it 
farms_phl_map <-  st_as_sf(phl_lat_lon, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_phl_map)
```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/crustaceans/crustacean_farms/data/crustacean_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)

write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
```

>>>>

Now we will map the remaining countries with crustacean farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or 
 dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it. We will gapfill later.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).

5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
 - country, species, n_existing_points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

## Indonesia
Can't find any infomration on crab farm locations in Indonesia. This will be fully gapfilled. data_quality = 1

@@

```{r}
idn_gf <- data.frame(iso3c = "IDN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(idn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_idn.csv"))

@@

Can't find any datasets of marine crustacean farm locations in China. This will be fully gapfilled. data_quality = 1

@@

```{r}
chn_gf <- data.frame(iso3c = "CHN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(chn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_chn.csv")) 
```

@@

@@

 - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.

```{r}
bgd_gf <- data.frame(iso3c = "BGD", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(bgd_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_bgd.csv")) 
```

@@

@@

 - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.

```{r}
mmr_gf <- data.frame(iso3c = "MMR", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(mmr_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_mmr.csv")) 
```

@@

 - Table on page 20: This is a table from 2004, but it will have to do. It also has production estimates, which is nice.

@@

 - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.

```{r}
vnm_gf <- data.frame(iso3c = "VNM", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(vnm_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_vnm.csv")) 
```

@@

@@

 - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.

```{r}
phl_gf <- data.frame(iso3c = "PHL", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
write_csv(phl_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_phl.csv")) 
```

### 2021-05-11 marine/salmon/salmon_farms/STEP1_fao_salmon_production.Rmd
made the figures!

sum(explore$fao_tonnes_production) # 2753752
sum(explore$percent) # 100.01
```

>>>>

sum(explore$fao_tonnes_production) # 2753752
sum(explore$percent) # 100.01

unique(explore$country) # - 16 countries 
```

```{r}
## write out bivalve taxa and production for Juliette
fao_salmon_taxa_prod <- fao %>%
  filter(species %in% salmon_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_salmon_taxa_prod$value) # 2754210 - adds 458 tonnes

unique(fao_salmon_taxa_prod$country) # 16 countries 
```
